Results

### 2019-09-20 analysis/03_analysis.Rmd
Visualize using geom_density_ridges.

```{r plot-marginals}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 1                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates, height = Theta)) + 
    # what other geoms could we use
    # - geom_ridgeline
    geom_ridgeline(fill="lightblue") +
    # - geom_density_ridges
    # - geom_halfeyeh
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}

# Notes to self:
# how to filter to zoom in on a certain part of the graph
# load the rethinking package and use the draws and summarize them
# we have the draws, sum/distribution of counts of samples of the posterior

>>>>

```{r plot-marginals}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 1                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
# zoom in on a certain part of the graph
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
# 1. geom_ridgeline 
    # geom_ridgeline(fill = "blue") +
# 2. geom_density_ridges seems to be the better option for overlapping distributions.
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.001) +
        # geom_density_ridges(scale = 3) - control overlap
        # geom_density_ridges2 - includes bottom line
        # geom_density_ridges(rel_min_height = 0.01) - shortens tails
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}

# Notes to self:

# load the rethinking package and use the draws and summarize them
# we have the draws, sum/distribution of counts of samples of the posterior
